% ***************************************************
% PRELIMINARY PAGES
% ***************************************************
% The instructions contained within this part of the thesis template need to be suppressed from the final thesis. There are instructions on how to do this in the MainThesis.tex file.

% To ensure your work is not suppressed with the instructions please add your text only where instructed.


%***Publications included in this thesis***
\noindent\textbf{\underline{Publications included in this thesis}}

\noindent\textbf{Conradsen, C.}, Blows, M. W., \& McGuigan, K. (2022). Causes of variability in estimates of mutational variance from mutation accumulation experiments. \textit{Genetics}, 221(2), iyac060. Incorporated as Chapter 2.

\begin{center}
\begin{tabular}{ll} 
\toprule
Contributor & Statement of contribution \\
 \hline
 Conradsen, C. (Candidate) & Conception and design (10\%)  \\ 
 & Analysis and interpretation (60\%)  \\ 
 & Drafting and Production (75\%)  \\[2ex] 
Blows, M. W. & Conception and design (40\%)  \\ [2ex]
McGuigan, K. & Conception and design (50\%)  \\ 
& Analysis and interpretation (40\%)  \\ 
 & Drafting and Production (25\%)  \\ 
 \bottomrule
\end{tabular}
\end{center}
\newpage

%***Submitted manuscripts included in this thesis***
\noindent\textbf{\underline{Submitted manuscripts included in this thesis}}\\
\bigskip
\noindent No manuscripts submitted for publication.\\
\vspace{36pt}

% %***Other publications during candidature***
\noindent\textbf{\underline{Other publications during candidature}}\\
\bigskip
\noindent\textbf{Conradsen, C.}, Walker, J. A., Perna, C., \& McGuigan, K. (2016). Repeatability of locomotor performance and morphology–locomotor performance relationships. \textit{Journal of Experimental Biology}, 219(18), 2888-2897.\\
\bigskip
\noindent Narayan, V. P., Wasana, N., Wang, Y., \& \textbf{Conradsen, C.} (2022). Digest: More than just a pretty fin: The evolution of sexual ornaments in killifish. \textit{Evolution}, 76(1), 184-186.\\
\vspace{36pt}

% \textbf{Example:}
% \subsection*{Conference abstracts}

% \begin{enumerate}

% \item \textbf{Your Name}, Co-author 1, and Final Author, Title of your conference paper, \textit{Proceedings of Conference}, other details.

% \end{enumerate}

% \subsection*{Book chapters}

% \begin{enumerate}

% \item \textbf{Your Name}, Co-author 1, and Final Author, Title of your chapter, Book, editor, etc.

% \end{enumerate}

% %***Contributions by others to the thesis***
\noindent\textbf{\underline{Contributions by others to the thesis}}\\
\bigskip
\noindent 
No contributions by others.\\

\vspace{36pt}
\noindent\textbf{\underline{Statement of parts of the thesis submitted to qualify for the award of another degree}}\\
\bigskip
\noindent 
No works submitted towards another degree have been included in this thesis.\\
\vspace{36pt}

\noindent\textbf{\underline{Research Involving Human or Animal Subjects}}\\
\bigskip
\noindent 
No animal or human subjects were involved in this research.\\
\newpage

\noindent\textbf{\underline{Acknowledgements}}\\
%%%%%%%%%% WRITE SUFF HERE %%%%%%%%%%%%%%%%%
\vspace{2cm}

I first would like to thank my supervisor, Associate Professor Katrina McGuigan because without her, this thesis would not have existed. I especially appreciated Katrina's dedication to helping and providing feedback (often seemingly at the drop of a hat), her patience (as it was a bumpy ride), her exceptional fly skills and guidance into the academic world. Over the last few years I have learnt so much from you.\par

I would like to thank my secondary supervisors, Professor Mark Blows and Professor Steve Chenoweth for their infectious enthusiasm for quantitative genetics. And, the force that made up the collective Chenoweth, McGugian and Blows labs. Yasmin Holden, Vikram Narayan, Derek Sun, Nicholas Appleton, Adam Reddiex, Ash Kanaan, Jessica McCarroll, Robert Dugand, Emma Hine, Robert Griffith, Julie Collect and Jaqueline Sztepanacz, I am forever thankful for the hours of fly lab help. I'll always remember fondly our chats whilst either pulling the millionth fly wing, making fly food, analysing data or sexing out males and females. Scott Allen, Yigan Wang and Nick Smith your bioinformatic wizardry made Chapter 4 possible. And I'd also like to take the opportunity to thank Tim Staples, Andrew Maynard, Andrew Mather, Maddie James, Hugo Perdomo, Theo Crawford, Tom Richards, Hern\'an C\'aceres and Rhys Parry for the odd bit of advice here or there. \par

This was a very long PHD and unsurprisingly there were many hurdles due both to the academic and personal side of things. I owe so much to Rebecca Mills, rescuing me from my lonely office at a time when I was particularly vulnerable. I will always remember the day of you bursting in, and then promptly frog-marching me to see Gail, and inviting me to join Kathy Ebert, Will Arnold and Tirosh Shapira in the haven that was the office-on-the-other-side-of the-wall. Similarly, mid-pandemic, when the world was at its most dystopic point; Zack McIntyre you were the best office nephew to have.  Russell Yong, you always provided unwavering faith and didn't shy away when the conversations headed to rocky terrain. And, to Lois Eden and the BIOL1020 tutoring crew, the evening classes were always the highlight of my day.\par

At the very foundation of it all, I couldn't have finished if it wasn't for the support of my family, Kelci, Tristan, Mom, Dad, Nadya Panagides and Cedric van den Berg. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\noindent\textbf{\underline{Financial support}}\\
\bigskip
\noindent 
This research was supported by an Australian Government Research Training Program Scholarship.\\
\bigskip
\noindent 
Chapters 2, 3 and 4 were supported by funding from the Australian Research Council awarded to
Katrina, McGuigan and Mark Blows.\\
\bigskip
\noindent
UQ Biological Sciences Conference Travel Award to C. Conradsen.\\
\vspace{36pt}

\noindent\textbf{\underline{Keywords}}\\
\bigskip
\noindent 
distribution of fitness effects, mutational variance, \textit{Drosophila serrata}, mutation accumulation, adaptive phenotype, mutation, Poolseq, M matrix
\vspace{36pt}

%***Australian and New Zealand Standard Research Classifications (ANZSRC)***
\noindent\textbf{\underline{Australian and New Zealand Standard Research Classifications (ANZSRC)}}\\
\bigskip
\noindent 

% Provide data that links your thesis to the disciplines and discipline clusters in the Federal Government’s Excellence in Research for Australia (ERA) initiative.\\

% \noindent
%http://www.abs.gov.au/Ausstats/abs@.nsf/Latestproducts/6BB427AB9696C225CA2574180004463E?opendocument

ANZSRC code: 060411 Population, Ecological and Evolutionary Genetics, 60\% \\
\indent ANZSRC code: 060412 Quantitative Genetics (incl. Disease and Trait Mapping Genetics), 40\% \\
\vspace{36pt}


%***Fields of Research (FoR) Classification***
\noindent\textbf{\underline{Fields of Research (FoR) Classification}}\\
% See http://www.abs.gov.au/Ausstats/abs@.nsf/Latestproducts/6BB427AB9696C225CA2574180004463E?opendocument}
\bigskip
FoR code: 0603, Evolutionary Biology, 80\% \\
\indent FoR code: 0604, Genetics, 20\% \\

% % ********* Enter your text below this line: ********


% % ***************************************************
